\documentclass[letterpaper,10pt]{article}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}
\setlength{\footskip}{4.08pt}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{BrickRed}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{BrickRed}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-12pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-3pt}}

\begin{document}

\begin{center}
  {\Huge \scshape Ayush Pandey} \\ \vspace{2pt}
  \small \raisebox{-0.1\height}\faPhone\ +91 9079293042~ \href{mailto:ayushpandey.job@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{ayushpandey.job@gmail.com}} ~
  \href{https://www.linkedin.com/in/ayushpandey003}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn.com/in/Ayushpandey003}} ~
  \href{https://github.com/AyushPandey003}{\raisebox{-0.2\height}\faGithub\ \underline{Github.com/AyushPandey003/}}
  \vspace{-6pt}
\end{center}

\vspace{-12pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{VIT Bhopal University, Bhopal}{2022 - 2026}{B.Tech in Computer Science \& Engineering}{8.7/10 CGPA}
\vspace{-2pt}
\resumeSubheading{Lucky Bal Niketan Senior Secondary School, Jodhpur}{2020 - 2022}{Intermediate XII (secondary)/High School X}{8.0/10.0; 8.98/10.0}
\resumeSubHeadingListEnd
\section{Technical Skills}
\textbf{Languages}: C++, C, Java, Python, TypeScript \\
\textbf{Web Development}: React, Angular, Node.js, HTML/CSS, Spring Boot \\
\textbf{Databases}: MySQL, MongoDB, PostgreSQL, Prisma, Drizzle, Spring Boot, Database Management Systems (DBMS) \\
\textbf{Concepts}: Object-Oriented Programming (OOP), Operating Systems, Computer Organization, Strong Communication \\
\textbf{Other}: Docker, Git, RESTful APIs
\vspace{4pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Ecommerce Website: Multi-vendor Ecommerce Platform}}{\href{https://grocify-admin.vercel.app}{\underline{Link}}}
\resumeItemListStart
\resumeItem{Engineered the frontend using \textbf{Next.js 13}, projecting a 40\% enhancement in page load speed through \textbf{server-side rendering (SSR)} and \textbf{static site generation (SSG)}.}
\resumeItem{Integrated \textbf{Prisma} for seamless database interactions, estimating a 25\% increase in query execution efficiency.}
\resumeItem{Integrated \textbf{Stripe} for secure payment processing, forecasting a 15\% reduction in transaction failure rates.}
\resumeItem{Planning to use \textbf{PostgreSQL} for database converting existing database of Mongo Db and using Drizzle ORM in place of Prisma For much Faster execution..}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ETCAM: Python-based Event Management Software}}{\href{https://github.com/AyushPandey003/Event-Ticketing-Certification-Generation-And-Auto-Mailer}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Developed \textbf{ETCAM}, a Python-based software that automates certificate generation, with potential to increase efficiency for large-scale events and can be used wherever ticket verification is needed.}
\resumeItem{Implemented \textbf{MD5 hashing} for secure ticket generation, ensuring unique and fraud-resistant event tickets, potentially reducing ticket fraud significantly.}
\resumeItem{Engineered an automated email notification system using \textbf{Google API}, enabling the distribution of personalized emails to a large number of participants, thus streamlining event communication.}
\resumeItem{Tested the application in an actual event, where it successfully managed email communications for 150 participants, demonstrating its reliability and effectiveness in real-world scenarios.}

\resumeItemListEnd

\resumeProjectHeading
{\textbf{Blog App: Full-Stack Blogging Platform}}{\href{https://github.com/AyushPandey003/Blog-Frontend}{\underline{In Progress}}}
\resumeItemListStart
\resumeItem{Developed a dynamic frontend using \textbf{Angular}, which enhances user interaction times and provides a smooth, responsive user experience across various devices.}
\resumeItem{Built robust and scalable RESTful APIs with \textbf{Spring Boot}, capable of handling high volumes of requests efficiently, ensuring the application's performance remains optimal under load.}
\resumeItem{Included  for creating, editing, and deleting blog posts, as well as user comments and likes, providing a comprehensive blogging platform with complete CRUD functionalities.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------

\section{Certific}
\resumeSubHeadingListStart
\resumeSubheading{\href{https://coursera.org/share/83316bef4316c272308747318915d125}{\underline{Google IT Professional Certificate}}}{January 2024}{Issued by Google}{}
\resumeItemListStart
\resumeItem{\textbf{IT Security: Defense against the Digital Dark Arts} — Google}
{Achieved a grade of 96.80\%. A course covering comprehensive IT security principles and practices.}
\resumeItem{\textbf{The Bits and Bytes of Computer Networking} — Google}
{Achieved a grade of 95\%. An in-depth study on the fundamentals and advanced concepts of computer networking.}
\resumeItem{\textbf{Successfully Completed Cloud Computing course By NPTEL} securing Silver certification with 75\% score.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Profiles/Achievements}
\resumeItemListStart
\resumeItem{Solved 250+ DSA problems from Rapid Growth Problemset, building strong problem-solving skills. \href{https://leetcode.com/u/coder_ayush_leet/}{Leetcode}, \href{https://www.geeksforgeeks.org/user/coder_ayush/}{GeeksForGeeks}}
\resumeItem{Qualified for second round in asyncs reimagine Hackathon by Sheriyans coding school around top 100 teams out of 750 teams.}
\resumeItemListEnd

\section{Leadership}
\resumeSubHeadingListStart
\resumeSubheading{President}{Aug 2022 – Present}{Linpack Club, VIT Bhopal University}{}
\resumeItemListStart
\resumeItem{Strategized and organized coding events and workshops, on Fake currency detection using matlab resulting in a 50\% increase in member participation and a 30\% rise in new memberships.}
\resumeItem{Mentored junior members, enhancing their coding skills and problem-solving techniques, leading to a 20\% improvement in club performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document} 